Activity Monitoring Assignment-1
=================================
1.Reading the data from the local directory into R
```{r}
activity<-read.csv("C:\\Users\\VIKASH\\Documents\\activity.csv",header=T)
```
Checking the class of the variables
```{r}
str(activity)
```
Transforming the date variable from factor to POSIXlt (class for date and time)
```{r}
activity$date<-strptime(activity$date,format="%Y-%m-%d")
```
2.Histogram of total number of steps taken each day
```{r}
steps_day<-aggregate(activity$steps,list(date=as.character(activity$date)),sum,na.rm=TRUE,na.action=NULL)
hist(steps_day$x,xlab="No of Steps",ylab="Frequency",main="Histogram of total no of steps taken per day")
```
Calculating the Mean and Median of total no of steps taken per day
```{r}
mn<-mean(steps_day$x,na.rm=TRUE)
md<-median(steps_day$x,na.rm=TRUE)
```
The mean is `r mn` and the median is `r md`

3.Time series plot of 5 minute interval period and average no of steps taken across all day
```{r}
steps_interval<-aggregate(activity$steps,list(interval=activity$interval),sum,na.rm=TRUE,na.action=NULL)
plot(steps_interval$interval,steps_interval$x,type="l",xlab="Interval",ylab="no of steps")
mx<-steps_interval[steps_interval$x==max(steps_interval$x),1]
```
Time Interval which has maximum no of steps on an average across all days is `r mx`

4.Calculating no of NAs
```{r}
no_na<-sum(is.na(activity$steps))
```
The total no of NAs in the original activity dataset is `r no_na`

5.We will use mean of that interval for imputing the missing values.
```{r}
new_activity<-activity
new_activity[is.na(new_activity)]=steps_interval$x
```
New histogramafter imputing missing values
```{r}
new_steps_day<-aggregate(new_activity$steps,list(date=as.character(new_activity$date)),sum,na.rm=TRUE,na.action=NULL)
hist(new_steps_day$x,xlab="No of Steps",ylab="Frequency",main="Modified histogram of total no of steps taken per day")
```
Calculating Mean and Median of new dataset
```{r}
new_mn<-mean(new_steps_day$x)
new_md<-median(new_steps_day$x)
```
The new mean is `r new_mn` and new median is `r new_md`
6.We will create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day
```{r}
var_day<-weekdays(new_activity$date)
l<-var_day=="Saturday"|var_day=="Sunday"
var_day[l]<-"Weekend"
var_day[!l]<-"Weekday"
var_day<-as.factor(var_day)
new_activity<-cbind(new_activity,var_day)
```
A panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis)
```{r}
new_steps_interval<-aggregate(steps~interval+var_day,data=new_activity,sum)
library(lattice)
xyplot(steps~interval|var_day,data=new_steps_interval,type="l",xlab="Interval",ylab="Number of Steps",layout=c(1,2))
```

